Mahotas: Open source software for scriptable computer vision

### 2012-08-30 paper.tex
TXT Add comparison with opencv

\begin{table}
\centering
\begin{tabular}{lrr}
\toprule
Operation & mahotas & pymorphy\\
\midrule
erode       &     9.90 &    13.06 \\
dilate      &    10.48 &     8.17 \\
open        &    20.26 &    21.05 \\
cwatershed  &   181.47 & 50211.56 \\
center mass &     6.39 &       NA \\
daubechies  &    16.92 &       NA \\
haralick    &   276.90 &       NA \\
\bottomrule
\end{tabular}
\caption{Efficiency Results for mahotas and pymorph. Shown are values as
multiples of the time that \code{numpy.max(f)} takes.}
\label{tab:efficiency}
\end{table}

@@

The comparison is against Pymorph~\citep{DougLotu:03}, which is a pure Python
implementation of some of the same functions. We can see that simple
morphological operations (erosion, dilation, opening) take a similar amount of
time in mahotas and pymorph (pymorph intelligently uses numpy operations for
these). However, some more complex operations such as watershed are much faster
in mahotas.

>>>>

\begin{table}
\centering
\begin{tabular}{lrrrrr}
\toprule
Operation & mahotas & pymorph & scikits-image & OpenCV\\
\midrule
erode       &     12.2 &     14.4 &     41.9 &      0.4 & \\
dilate      &     13.4 &      9.0 &     39.4 &      0.4 & \\
open        &     25.6 &     23.4 &     81.3 &       NA & \\
center mass &      7.1 &       NA &       NA &       NA & \\
sobel       &     81.9 &       NA &    106.5 &      6.2 & \\
cwatershed  &    194.8 &  56928.5 &    288.9 &     42.9 & \\
daubechies  &     20.7 &       NA &       NA &       NA & \\
haralick    &    326.9 &       NA &   7497.4 &       NA & \\
\bottomrule
\end{tabular}
\caption{Efficiency Results for mahotas, pymorph, scikits-image, and openCV
(through Python wrappers). Shown are values as multiples of the time that
\code{numpy.max(f)} takes.}
\label{tab:efficiency}
\end{table}

@@

The comparison is against Pymorph~\citep{DougLotu:03}, which is a pure Python
implementation of some of the same functions; scikits-image, which is a similar
project to mahotas, but with a heavier emphasis on the use of
Cython~\citep{Cython}; and OpenCV, which is a \cpp{} library with automatically
generated Python wrappers.

OpenCV is the fastest library, but this comes at the cost of some flexibility.
Arguments to its functions must be of the exact expected type and it is
possible to crash the interpreter if types do match the expected type (in the
other libraries, all types are checked and an exception is generated which can
be caught by user code). This is particularly relevant for interactive use.

Among the other libraries, mahotas is the fastest, except when comparing simple
morphological operations with pymorph. Pymorph intelligently uses arithmetic
operations for this operation and can be very fast. However, for more complex
methods, such as watershed; its pure Python approach is very inefficient.
